Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-06-16 ms.tex
a few notes on the OTIS dark tests

\begin{deluxetable*}{ccc}[b!]
\tablecaption{Summary of Noise Sources in Weak Lens +8 Aperture Dark Test}\label{tab:noiseSummaryWLP8}
\tabletypesize{\footnotesize}
%\tablecolumns{7}
%\tablenum{2}
\tablewidth{0pt}
\tablehead{
\colhead{Noise Description} &
\colhead{$\sigma$} &
\colhead{$\sigma$} \\
\colhead{} &
\colhead{DN} &
\colhead{ppm}\\
}
\startdata
Ideal Photon Noise & 4,400 & 113 \\
Ideal Uncorrelated Read Noise & 1,300 & 33 \\
\hline
Measured Read Noise (no correction) & 23,500 & 600 \\
Measured Read Noise (reference pixel correction) & 10,800 & 280 \\
Measured Read Noise (reference channel subtraction) & 9,700 & 250 \\
Measured Read Noise (row-by-row median subtraction) & 6,000 & 150 \\
Measured Read Noise (20 Component PCA subtraction) & 5,400 & 140 \\
Measured Read Noise (smoothed 40 px kernel) & 900 & 23 \\
\enddata
\tablecomments{The theoretical and measured noise sources in one integration for a Weak Lens +8 Time Series.
The noise is the sum within a 70 pixel radius source aperture and 75 to 100 pixel background aperture (in DN) or relative to the photon signal (in ppm).
The integration is assumed to be a bright source with 2 groups of 1 integration each up the ramp (Correlated Double Sampling or CDS mode).}
\end{deluxetable*}

@@

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{pca_dark_amp_all_grp54.pdf}
\includegraphics[width=.4\columnwidth]{pca_dark_amp_all_grp55.pdf}
\caption{Principal component eigenvectors identified from group 54 (left) and group 55 (right).
}\label{fig:pcaEigenvectors}
\end{figure*}

@@

After experimenting with these configurations, we find the following pipeline steps are important:
\begin{itemize}
	\item Fitting a line up the ramp gives superior results to subtracting the last and first pairs of read (as expected by reducing the photon noise)
	\item Centering the aperture with the central spot inside the hexagon is important to conserve the flux within the aperture
	\item Row-by-row subtraction (along the detector's fast-read direction) gives superior background subtraction to traditional aperture photometry (using the mean or robust average value in a background annulus)
	\item Aperture sizes for the source at ~70 pixels, outside the hexagon, gave the best precisions
	\item An annulus aperture on the source (including the inner and outer edges of the hexagonal PSF) usually gives the best precision light curves
\end{itemize}

@@

\begin{figure*}
\gridline{\fig{wlp8_otis_psf.pdf}{0.7\textwidth}{WLP8 Image} }
\gridline{\fig{{grism_otis_psf.pdf}}{0.7\textwidth}{Grism Image}}
\caption{Median images of the short wavelength (SW) weak lens mode and long wavelength (LW) grism spectroscopy that were used simultaneously in a grism time series stability test.
Due to the OTIS optics setup, the short wavelength WLP8 image does not nearly represent the hexagonal PSF from CV3 (Figure \ref{fig:WLP8PSF}) or flight.
}\label{fig:otisPSFs}
\end{figure*}

>>>>

\begin{deluxetable*}{ccc}[b!]
\tablecaption{Summary of Noise Sources in Weak Lens +8 Aperture Dark Test}\label{tab:noiseSummaryWLP8}
\tabletypesize{\footnotesize}
%\tablecolumns{7}
%\tablenum{2}
\tablewidth{0pt}
\tablehead{
\colhead{Noise Description} &
\colhead{$\sigma$} &
\colhead{$\sigma$} \\
\colhead{} &
\colhead{DN} &
\colhead{ppm}\\
}
\startdata
Ideal Photon Noise & 4,400 & 113 \\
Ideal Uncorrelated Read Noise & 1,300 & 33 \\
\hline
Measured Read Noise (no correction) & 23,500 & 600 \\
Measured Read Noise (reference pixel correction) & 10,800 & 280 \\
Measured Read Noise (reference channel subtraction) & 9,700 & 250 \\
Measured Read Noise (row-by-row median subtraction) & 6,000 & 150 \\
Measured Read Noise (20 Component PCA subtraction) & 5,400 & 140 \\
Measured Read Noise (smoothed 40 px kernel) & 900 & 23 \\
\enddata
\tablecomments{The theoretical and measured noise sources in one integration for a Weak Lens +8 Time Series.
The ppm units are assuming a 60\% well depth or 3.9$\times 10^7$ DN during an integration.
The noise is the sum within a 70 pixel radius source aperture and 75 to 100 pixel background aperture (in DN) or relative to the photon signal (in ppm).
The integration is assumed to be a bright source with 2 groups of 1 integration each up the ramp (Correlated Double Sampling or CDS mode).}
\end{deluxetable*}

@@

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{pca_dark_amp_all_grp54.pdf}
\includegraphics[width=.4\columnwidth]{pca_dark_amp_all_grp55.pdf}
\caption{The first 10 principal component eigenvectors identified from group 54 (left) and group 55 (right).
}\label{fig:pcaEigenvectors}
\end{figure*}

@@

After experimenting with these configurations, we find the following pipeline steps are important:
\begin{itemize}
	\item Fitting a line up the ramp gives superior results to subtracting the last and first pairs of read (as expected by reducing the read noise)
	\item Centering the aperture with the central spot inside the hexagon is important to conserve the flux within the aperture
	\item Row-by-row subtraction (along the detector's fast-read direction) gives superior background subtraction to traditional aperture photometry (using the mean or robust average value in a background annulus)
	\item Aperture sizes for the source at ~70 pixels, outside the hexagon, gave the best precisions
	\item An annulus aperture on the source (including the inner and outer edges of the hexagonal PSF) usually gives the best precision light curves
\end{itemize}

@@

\begin{figure*}
\gridline{\fig{wlp8_otis_psf.pdf}{0.7\textwidth}{WLP8 Image} }
\gridline{\fig{{grism_otis_psf.pdf}}{0.7\textwidth}{Grism Image}}
\caption{Median images of the short wavelength (SW) weak lens mode and long wavelength (LW) grism spectroscopy that were used simultaneously in a grism time series stability test.
Due to the OTIS optics setup, the short wavelength WLP8 image does not nearly represent the hexagonal PSF from CV3 (Figure \ref{fig:WLP8PSF}) or flight.
We perform photometry on a single knot of emission as highlighted as the blue circular aperture.
For the grism time series, we use a rectangular aperture and a vertically offset background box.
}\label{fig:otisPSFs}
\end{figure*}
